---
title: "Demonstration"
output: html_notebook
---

First, lets load the package into R!
```{r}
install.packages("colourpicker")
library(colourpicker)
```
**Now, what are the functions of "colourpicker"?**

* **colourInput:** 
    + Creates a color input widget such that users to pick colors in an R Shiny app.  
* **updateColourInput:**
    + Allows R Shiny user to change colourInput settings
* **colourWidget:** 
    + Creates a color input widget for html documents
* **colourPicker:** 
    + Gadget that allows an RStudio user to easily pick and find colors in R.
* **plotHelper:**
    + Gadget that allows an RStudio user to directly try out different color combinations for a plot.   
* **runExample:**
    + Allows user to see example widgets
    
**Okay, which ones do we care about? "colourInput," "colourPicker," and "plotHelper"? Okay!**

**First, let's start with colourInput.** Actually, let's first discuss what the "shiny" package is:
```{r}
if (interactive()) {
runExample()
}
```

Okay...where does "colourInput" fit into all of this?
```{r}
colourInput(inputId, label, value = color, showColour = c("both", "text", "background"), palette = c("square", "limited"), allowedCols = NULL, allowTransparent = FALSE, returnName = FALSE)
```
Here's an example of what it looks like: 
https://daattali.com/shiny/colourInput/

Wow...that's a little too complex for our class! What's something in this package a novice like I can use?

**How about "colourPicker"?**
Let's see what's in our Addins menu...
```{r}
if (interactive()) {
cols <- colourPicker()
}
```
...Oooh! Nice!

**What about plotHelper**?
Again, let's see what's in our Addins menu...Ah! okay. Let's try some code of our own:
```{r}
library(tidyverse)
library(utf8)
anti<-read.csv("yup.csv", check.names = F)
anti=mutate(anti, avg=(pen+strep+neo)/3)
anti=arrange(anti, avg)

ggplot(data=anti) +
  geom_point(size=3, mapping = aes(x=strep, y=reorder(abbr, -avg), shape = gram, color="Streptom"), position = position_nudge(x = 0.04)) +
  geom_point(size=3, mapping = aes(x=pen, y=reorder(abbr, -avg), shape = gram, color="Penicilin")) +
  geom_point(size=3, mapping = aes(x=neo, y=reorder(abbr, -avg), shape = gram, color="Neomycin")) +
  scale_x_continuous(trans='log10') +
  scale_color_manual(values=c("Streptom"="orange", "Penicilin"="blue", "Neomycin"="violetred3")) +
  scale_shape_manual(values=c(17,16)) +
  labs(title="Burtin's Bacteria", x = "Minimum Inhibitory Concentration (MIC)", y = "Bacteria", color =
  "Antibiotics", shape= "Gram Staining") +
  theme(plot.title = element_text(hjust = 0.5))
```

